Stability And Performance Of Virtual Aggregations Of Prosumers Through Diversification In The Smart Grid

### 2015-07-31 Article.tex
update

In order not to overload the market with unrealistically small coalitions, the grid operator also specify a lower bound $ P^{MIN} $ on the contract values. We thus characterized a valid coalition as one satisfying the two conditions :

@@

The Gaussian assumption of this small example is convenient as it allows us to write $ P_{S}^{CRCT \star} $ analytically. Nevertheless, such assumption is rather unrealistic in practice. In the following, we keep the same framework but release this Gaussian assumption unless the contrary is specified. This assumption will indeed be convenient for computing some parameter estimates.

>>>>

In order not to overload the market with unrealistically small coalitions, the grid operator also specifies a lower bound $ P^{MIN} $ on the contract values. We thus characterized a valid coalition as one satisfying the two conditions :

@@

The Gaussian assumption of this small example is convenient as it allows us to write $ P_{S}^{CRCT \star} $ analytically. Nevertheless, such assumption is rather unrealistic in practice. In the following, we keep the same framework but release this Gaussian assumption unless the contrary is specified (see eq. \ref{eq:alpha_star}). This assumption will indeed be convenient for computing some parameter estimates.
